Adopting agile in the large: motivations, success factors and challenges

### 2014-04-29 journal/article.tex
Challenge: lack of physical spaces

% Old work and commitments

@@

>>>>

% Old work and commitments, schedule pressure

@@

% Physical spaces, challenge of finding a seating

In some cases the old way of working had people seated physically distributed,
in opposite to what agile methods typically suggest. Office spaces needed to be
arranged so that the entire team could work in a single room, but it took time
and effort, and it was not always possible [P36, P6]. Lewis and Neher describe
how dedicated rooms for teams could not be arranged, and team events such as
daily standups required booking a conference room [P29]. In another case the
estate organization shut down the teams' attempts to modify working spaces
[P49].
